The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-20 draft/ms.tex
Proofread complete.

Since \cite{Wright2011}, as more planets were robustly discovered by
different methods other than radial velocity and transit, we have
expanded our database at exoplanets.org to better ingest those
planets.

% KOIs
First, we now include the KOIs discovered by \kepler\ in the
EDE. Although KOIs are not counted as part of the EOD due to their
status of being ``candidates", we include them in our website so that
these KOIs are put into the context of all confirmed exoplanets. The
KOIs listed in our table include three Kepler data releases (as of
March 2014), and we always keep up with the most up-to-date
releases. The original data are from the NASA Exoplanet Archive.

@@

\end{itemize}
Some of the exoplanets primarily detected by these methods do not have
well-determined orbital parameters, and thus they are categorized as
``Other Planets'' on exoplanets.org instead of being in the EOD. These
planets can be displayed by check the `Other' option for the EDE
table. As of March 2014, no microlensing or imaging planets are in the
EOD, while several timing exoplanets have well-determined orbital
parameters and are included in the EOD. Moreover, there have been no
astrometry planets in the EOD but we plan to include them if any
robust detections occur.

>>>>

Since \cite{Wright2011}, as \kepler\ has discovered many exoplanet
candidates, and more planets were robustly discovered by various
methods though not having very well characterized orbits, we have
expanded exoplanets.org to ingest those planets for the convenience of
the users and also to keep our database complete in terms of confirmed
exoplanets.

% KOIs
First, we now include the KOIs discovered by \kepler\ in the
EDE. Although KOIs are not counted as part of the EOD due to their
status of being ``candidates", we include them in our website so that
these KOIs are put into the context of all confirmed exoplanets. The
KOIs listed in our table include three \kepler\ data releases (as of
March 2014), and we always keep up with the most up-to-date
release. The original data are from the NASA Exoplanet Archive.

@@

\end{itemize}
Some of the exoplanets that are primarily detected by these methods do
not have well-determined orbital parameters, and thus they are
categorized as ``Other Planets'' on exoplanets.org instead of being in
the EOD. These planets can be displayed by check the `Other' option
for the EDE table. As of March 2014, no microlensing or imaging
planets are in the EOD, while several timing exoplanets have
well-determined orbital parameters and are included in the
EOD. Moreover, there have been no astrometry planets in the EOD but we
plan to include them if any robust detections occur.
